Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-12 outputs/paper/paper.qmd
Update paper.qmd

In panel B of @fig-bratepop-graph has three different subgroups. Race and ethnicity is subdivided into three sections, Hispanic, Black, and White. Both white and black are non-Hispanic population.

>>>>

Note that the data set is gathered as of 1989 for the race and ethnicity subgroup population, thus the x-axis of the graph starts from 1989. In panel B of @fig-bratepop-graph has three different subgroups. Race and ethnicity is subdivided into three sections, Hispanic, Black, and White. Both white and black are non-Hispanic population. The white population group shows relatively linear fashion compared to other population groups while the birth rates of Hispanic and Black population groups drastically drop over the 10 years from 1989 to 2000. Then another significant drop happened as of 2007 only in Hispanic population group. The change in births per 1,000 women in race and ethnicity population subgroup varies, 7.3, 25.8 and 42.1 in White, Black, and Hispanic group respectively.
